
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.

```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
library(gganimate)
library(gifski)
df <- read_csv('C:/Users/student/OneDrive - Bryant University/Documents/R/Math421/adult_census.csv')
df %>% ggplot(aes(x = age,
                  y = education.num, color = sex))+
    geom_point()+
    transition_states(marital.status)+
    labs(title = 'Status: {closest_state}')

```


2. Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.

```{r}
df %>% ggplot(aes(x = sex,
                  fill=race))+
  geom_bar(position = 'fill')+
  transition_states(marital.status)+
  labs(title = 'Status: {closest_state}')
```

3. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.

```{r}
library(lubridate)
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')

df$month <- month(df$Date_reported)
d1 <- df %>% group_by(month, Country) %>% summarise(mean = mean(Cumulative_deaths))
d2 <- d1 %>% group_by(month) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month {closest_state}', x='', y='Total Number of Deaths', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(month)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

4. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 

```{r}
df <- read_csv('https://covidtracking.com/data/download/all-states-history.csv')
df <- df %>% filter(deathIncrease>0, positiveIncrease>0)
library(lubridate)
df$month <- month(df$date)
d1 <- df %>% group_by(month, state) %>% summarise(mean = mean(death))
d2 <- d1 %>% group_by(month) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 8)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=state, fill=state, label=state)) + geom_col()+
    geom_text(aes(y = mean, label = state), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month {closest_state}', x='', y='Total Number of Deaths', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(month)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```
