
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|

```{r}
df = data.frame(Rank = c('0','1','2','3'), Age = c('28','34','29','42'), Name = c('Tom','Jack','Steve','Ricky'))
```


2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).

2. Show the names of the variables in the data

```{r}
 df <- read.csv('us-states.csv')
 names(df)
```


3. How many columns and rows the data have? 

```{r}
nrow(df)
ncol(df)
```


4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?

```{r}
sum(is.na(df))
colSums(is.na(df))
colMeans(is.na(df))
```


5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 

```{r, eval=FALSE}
class(df$Date)
df$Date = as.Date(df$Date)
class(df$Date)
```


6. Capitalize the names of all the variables

```{r}
names(df)[1] <- 'Date'
names(df)[2] <- 'State'
names(df)[3] <- 'Fips'
names(df)[4] <- 'Cases'
names(df)[5] <- 'Deaths'
```


7. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
mean(df$Cases, na.rm=TRUE)
max(df$Cases, na.rm=TRUE)
```


8. How many states are there in the data?  

```{r}
table(df$State)
length(table(df$State))
```


9. Create a new variable `weekdays` to store the weekday for each rows. 

```{r, eval=FALSE}
df$Weekdays <- weekdays(df$Date)
```


10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
- `no_death` if there is no death that day

```{r}
df$death2 <- ifelse(df$Deaths>0, 'has_death','no_death')
table(df$death2)
```


Find the frequency and relative frequency of `no_death` and `has_death`.

```{r}
freq <- table(df$death2)
rf <- table(df$death2)/length(df$death2)
```


11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)

```{r}
summary(df$Deaths)
```


12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r, eval=FALSE}
df$death3 <- case_when(df$Deaths<=846 ~ 'low_death',df$Deaths<=4101 ~ 'mid_death', TRUE ~ 'high_death')
table(df$death3)
```


13. Find the average cases in Rhode Island in 2021

```{r}
dfg <- df[(df$State=='Rhode Island')&(df$Date>='2021-01-01')&(df$Date<'2022-01-01'),]
mean(dfg$Cases)
```


14. Find the median cases by weekdays in Rhode Island in 2021 

```{r, eval=FALSE}
dfg1 <- df[(df$State=='Rhode Island'),]
by(df$Cases,df$Weekdays,median)
```


15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 

```{r}
dfg2 <- df[(df$State=='Rhode Island')&(df$Date>='2021-06-01')&(df$Date<'2021-10-01'),]
dfg2$Month <- substr(dfg2$Date,6,7)
by(dfg2$Cases,dfg2$Month,median)
```


16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when

```{r, eval=FALSE}
titanic <- read.csv('titanic.csv')
str(titanic)
names(titanic)
mean(titanic$Fare)
max(titanic$Fare)
min(titanic$Fare)
table(titanic$Sex)
is.na(titanic)
colSums(is.na(titanic))
class(titanic$Sex)
cor(titanic$Sex, titanic$Survived)
by(titanic$Pclass, titanic$Survived, FUN = mean)
titanic$Old <- ifelse(titanic$Age<20,"child","adult")
table(titanic$Old)
titanic$Maturity <- case_when(titanic$MIN<=12 ~ 'child', titanic$MIN<=21 ~ 'teenager',TRUE ~ 'adult')
```


17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

```{r, eval=FALSE}
titanic$Old <- ifelse(titanic$Age<20,"child","adult")
table(titanic$Old)
titanic$Country <- case_when(titanic$Embarked ='C' ~ 'Germany', titanic$Embarked ='S' ~ 'England', titanic$Embarked ='Q' ~ 'England')
```


If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
